TacticToe: Learning to Prove with Tactics

### 2018-02-20 tactictoe_jv.tex
removing early results for terms

Our default algorithm relies on argument predictions for theorems with a
radius of 16. It uses the produced list
$\mathit{Predictions}^{\mathit{tactic}}_{16}(g)$ to replace all the
placeholders
in $\hat{t}$.
The type of theorem lists is a very common type in \holfour proofs and theorems contain
enough information to be predicted accurately.
We also have positive results with term abstraction and plan to include it soon
in our default algorithm.

@@

%\subsection{Recent improvements}\todo{maybe remove this subsection}
%The final results could be improved by a few percent by including the
%following additional techniques that are already available.
%The technique already discussed in Section~ would most likely improve the
%results by 2-3 percent. Reducing the exploration coefficient from 4 to 2 would
%also probably give a 3 percent increase in the number of proven theorems as
%shown by a recent 1 in 10 evaluation on the full library.

\paragraph{Self-learning}\todo{explain better or remove or move to future work}
All our feature vectors have been learned form human proofs. We now can now
also add tactic-goal pairs that appears in final \tactictoe's proof. To prevent
duplication of effort, orthogonalization of those
tactics is essential to have a beneficial effect.
Since recording and re-proving are intertwined, the additional data is
available for the next proof search.
The hope is that the algorithm will improve faster by learning from its own
discovered proofs than from the human proof
scripts~\cite{DBLP:conf/cade/Urban07}. Side experiments indicate that
self-learning improves \tactictoe's success rate by less than one percent.

\subsection{Complexity of the proof search}

\pgfplotscreateplotcyclelist{my black}{
solid, mark repeat=100, mark phase=0, black!100\\
dashed, mark repeat=100, mark phase=0, black!100\\
}

>>>>

Our default algorithm relies on argument predictions for theorems with a
radius of 16. It uses the produced list
$\mathit{Predictions}^{\mathit{tactic}}_{16}(g)$ to replace all the
placeholders
in $\hat{t}$.
The type of theorem lists is a very common type in \holfour proofs and theorems contain
enough information to be predicted accurately.

%We have positive results 
%with term abstraction but they are not evaluated in 
%Section~\ref{sec:evaluation}.

@@

\paragraph{Reinforcement learning}
All our feature vectors have been learned form human proofs. We now can now
also add tactic-goal pairs that appears in final \tactictoe's proof. To prevent
duplication of effort, orthogonalization of those
tactics is essential to have a beneficial effect.
Since recording and re-proving are intertwined during evaluation, the 
additional data is available for the next proof search.
The hope is that the algorithm will improve faster by learning from its own
discovered proofs than from the human proof
scripts~\cite{DBLP:conf/cade/Urban07}. Side experiments indicate that
this one shot reinforcement learning method increases \tactictoe's success rate 
by half a percent.

\subsection{Complexity of the proof search}
\pgfplotscreateplotcyclelist{my black}{
solid, mark repeat=100, mark phase=0, black!100\\
dashed, mark repeat=100, mark phase=0, black!100\\}
